Searching for long-period transiting planets in the \kepler\ light curves using supervised classification

### 2015-04-08 document/ms.tex
WORDS

\newcommand{\paper}{\textsl{Article}}

@@

\paragraph{Generate the training \& validation sets}

We need to train the classification model on simulated signals.
To simulate these training and validation examples, we randomly select
sections of 121 contiguous flux measurements and simulate the transit signal
induced by the physical orbit of a large planet.
The specific distribution of simulated parameters is listed in \dfmtodo{some
table}.
In the simulations, we take limb darkening and integration time into account
\dfmtodo{cite}.
Since we expect most of the systematic variability to be time-reversible, we
augment the training set with simulations injected into the reversed time
series \citep[for example][]{Dieleman:2015}.
The training set also includes an equal number of negative examples---time
series chunks of the same length without a simulated transit injection.
By virtue of the fact that we are specifically searching for single transits
it is safe to assume that none of the negative samples from the other light
curve sections will have no transits.

We also generate a validation set of simulated signals.
This set is identical to the training set except it is simulated in sections
of light curve that are not used for training.
As discussed below, this set is used to determine the transit significance
threshold required to achieve a pure sample.

In practice, we only need to train three models on the three disjoint
training sets and then for each model, we validate and test on both of the
remaining splits.

\paragraph{Feature selection}

>>>>

\newcommand{\paper}{article}

@@

The following \sectionname s detail the application of this search procedure
from the training set simulations through to the candidate selection.
These candidates are then vetted by hand although more robust methods should
be possible as discussed in \sect{vetting}.
Finally, \sect{features} explores alternative representations of the data or
features.

\subsection{Splitting the dataset}

It is crucial that the model used to test for transits in a raw \kepler\
light curve not be trained on the same data.
We must split the light curve of each star into 3 disjoint sets.
For the model to work well, we require that the signals induced by
variability, noise, and other systematics be consistent between splits.
It is, therefore, necessary that we assign the splits carefully.
As discussed in \sect{data}, a light curve can be separated naturally into
``sections'' of contiguous measurements; these are the base unit for splitting
the dataset.
For the typical \kepler\ target, this division is finer than month long
chunks and there are about 100 sections for each light curve.
Each light curve section is cut out of a specific ``quarter'' and each quarter
was observed during a specific ``season''.

These divisions are relevant to this discussion because the spacecraft
pointing across a quarter was extremely precise and the photometric aperture
is fixed to the same pixels for the full quarter.
Therefore, the instrumentally-induced systematics tend to be qualitatively
consistent on quarter-long time scales.
Every three months, the \kepler\ spacecraft rolled by 90~degrees causing the
stars to end up on a different detector every quarter.
This means that while the astrophysical variability should be shared between
quarters at some level, the instrumental effects can be very different.
A year later, however, the spacecraft returned to the original pointing.
As a result, the data quality is also similar for observations made in the
same season.

In order to take advantage of the natural structure of the observations, we
try to evenly distribute observations from each quarter and season across the
three sets.
When this is not possible (with Quarter 0, for example), we randomly assign
the section to a split.

\subsection{Transit simulations}

As mentioned previously, we train the RF classification models on a set
simulated transit signals injected into real light curves and a set of light
curve sections assumed to contain no transits.
For each data split, we construct a set of 20,000 \texttt{transit} samples and
an equal number of \texttt{no transit} examples.
Each of these samples is generated by randomly selecting a section of 201
contiguous flux measurements from the split.
Since we expect most of the systematic variability to be symmetric in time, we
augment the training set by reversing the time series for half of the samples.
This is analogous to image processing methods that exploit rotation and
translational symmetries \citep[for an example from astronomy
see][]{Dieleman:2015}.

To generate the \texttt{transit} examples, we simulate the transit signal
induced by the physical orbit of a large planet.
The specific distribution of simulation parameters is listed in \dfmtodo{some
table}.
In these simulations, we take limb darkening and integration time into
account\footnote{\url{https://github.com/dfm/transit}}
\citep{Mandel:2002, Kipping:2010}.
For the purposes of this \paper, we only simulate circular orbits under the
assumption that a single transit of a planet on an elliptical orbit would be
nearly identical to a circular orbit at a different period.

\subsection{Initial candidate detection}

\subsection{Candidate vetting}\sectlabel{vetting}

\subsection{Feature selection}\sectlabel{features}
